A Novel Model-Free Learning Approach for Dynamic Target Tracking Problem and its Validation using Virtual Robot Experimentation Platform

### 2020-06-29 paperMIC2020/paperIEEE-MIC2020-V1.tex
added simulation figure

% The newly computed critic weights $\boldsymbol{\omega}$ are used to reconstruct the matrix ${\bf P}$ (i.e., updating the solving value function and hence calculating the associated policy) such that 
 %
 \begin{center}
 ${\bf P}=\begin{bmatrix} 
 2\,\omega^{1}    & \omega^{2}      & \omega^{3}       & \omega^{4}        \\ 
 \omega^{2}       &2\, \omega^{5}   & \omega^{6}       & \omega^{7}        \\
 \omega^{3}       & \omega^{6}      &2\, \omega^{8}   & \omega^{9}   \\   
 \omega^{4}       & \omega^{7}      & \omega^{9}      & 2\,\omega^{10}      
 \end{bmatrix}\in \mathbb{R}^{4\times 4},$
 \end{center}
 %
 where $\omega^{i}$ is the $i^{th}$ entry of the weight vector $\bm{\omega}.$ 
 \todo[inline]{merge the actor weights discussion with the rest}
 The critic wegihts are then used to update the actor weights which maps the state error to the desired ploicy (control actions) at every time step $t$ with the following equation:
 \begin{align}
 \label{eq:actorWeightsPolicy}    
 \mathbf{u}_k  =  \mathbf{\omega_a^{T}} \mathbf{e}_k
 \end{align}   
 Applying a similar gradient descent approach as with the critic weights the actor weights are updated as follows:
\begin{align}
   \bm{\omega_a}^{[r+1]} = \bm{\omega}^{[r]} - \ell_a(\mathbf{u}_k-\mathbf{u}_k^*)\mathbf{e}_k, 
 \label{eq:actorWeights}
 \end{align}
 where $\ell$ is the actor learning rate. 
 \\
 The complete policy iteration solution process for the leader-follower problem is detailed out in Algorithm \ref{alg:ModelFreeTracking}. %
 %
 \begin{algorithm2e}
     \caption{\label{alg:ModelFreeTracking} Model-free actor-critic reinforcement learning using the policy iteration solution.}
     \DontPrintSemicolon
     \KwIn{Sampling-time $T_s,$ $\mathbf{Q},~\text{and}~\mathbf{R}$ }
     \KwOut{Error trajectory $\mathbf{e}_k,$ for $k=0,1,\ldots$}
     % \KwData{Map representation using occupancy grid technique}
     % \KwResult{output******************************}
     \Begin{
         $k=0, r = 0$ \tcc*[h]{Discrete time and policy indices}\;
         $\eta = (n+m)(n+m+1)/2$\;
         Initialize $\mathbf{P}^{[0]}$ \tcc*[h]{Positive definite}\;
                 Set offset distance $d$\;
                 Given approximate initial poses of leader and follower, compute $\mathbf{e}_0$ using error model~\eqref{eq:stateError}\;
                 Compute follower's input $\mathbf{u}_0^{[0]}$ using policy~\eqref{eq:actorWeightsPolicy}\;
         \Repeat(\tcc*[h]{Main timing loop}){Tracking errors are zero}
         {
             Find $\mathbf{e}_{k+1}$ using~\eqref{eq:stateError}\;
             Compute policy $\mathbf{u}_{k+1}^{[r]}$ using~\eqref{eq:actorWeightsPolicy}\;
             %Evaluate and record Equation~\eqref{eq:modelFreeMatrixSolution}\;
             \If{[$(k+1)~\mathrm{modulo}~\eta]==0$ }
             {
                 $r\leftarrow r+1$\tcc*[h]{Evaluate policy}using~\eqref{eq:modelFreePolicy}\;
                 Solve for the critic-weights $\bm{\omega_c}$ using~\eqref{eq:criticWeights}\;
                 Solve for the actor-weights $\bm{\omega_a}$ using ~\eqref{eq:actorWeights}\;\;
                 Construct matrix $\mathbf{P}^{[r]}$ using vector $\bm{\omega_c}$\;
 %                \eIf{$\|\mathbf{P}^{[r]} - \mathbf{P}^{[r+1]}\|<\varepsilon$}{Set $\mathbf{u}_{k+1}^*\leftarrow\mathbf{u}_{k+1}^{[r]}$}{$k\leftarrow k+1$ }
             }
 %        {
 %                $k\leftarrow k+1$
 %            }
         $k\leftarrow k+1$
         }
     }
 \end{algorithm2e}

@@

 \begin{figure*}[htbp]%
 \subfigure[][]{%
    \label{fig:trajectoryRandom}%
    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/trajectoryRandomPathDistance.eps} }
\subfigure[][]{%
    \label{fig:stateErrorRandom}%
    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/stateErrorRandomPathDistance.eps} }
\\
 \subfigure[][]{%
    \label{fig:controlInputsRandom}%
    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/controlInputRandomPathDistance.eps} }
 \subfigure[][]{%
    \label{fig:weightRandomDistance}%
    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/weightRandomPathDistance.eps} }
\caption[Leader-follower performance for random trajectory.]{Performance in tracking random trajectory: 
  \subref{fig:trajectoryRandom} leader-follower trajectories,~\subref{fig:stateErrorRandom} state error,~\subref{fig:controlInputsRandom} linear speed and steering angle of the follower; and    \subref{fig:weightRandomDistance} learning weights.}%
  \label{fig:peformanceRandomTrajectory}%
\end{figure*}

>>>>

% The newly computed critic weights $\boldsymbol{\omega}$ are used to reconstruct the matrix ${\bf P}$ (i.e., updating the solving value function and hence calculating the associated policy) such that 
 %
 \begin{center}
 ${\bf P}=\begin{bmatrix} 
 2\,\omega^{1}    & \omega^{2}      & \omega^{3}       & \omega^{4}        \\ 
 \omega^{2}       &2\, \omega^{5}   & \omega^{6}       & \omega^{7}        \\
 \omega^{3}       & \omega^{6}      &2\, \omega^{8}   & \omega^{9}   \\   
 \omega^{4}       & \omega^{7}      & \omega^{9}      & 2\,\omega^{10}      
 \end{bmatrix}\in \mathbb{R}^{4\times 4},$
 \end{center}
 %
 where $\omega^{i}$ is the $i^{th}$ entry of the weight vector $\bm{\omega}.$ 
 \todo[inline]{merge the actor weights discussion with the rest}
 The critic wegihts are then used to update the actor weights which maps the state error to the desired ploicy (control actions) at every time step $t$ with the following equation:
 \begin{align}
 \label{eq:actorWeightsPolicy}    
 \mathbf{u}_k  =  \mathbf{\omega_a^{T}} \mathbf{e}_k
 \end{align}   
 Applying a similar gradient descent approach as with the critic weights the actor weights are updated as follows:
\begin{align}
   \bm{\omega_a}^{[r+1]} = \bm{\omega}^{[r]} - \ell_a(\mathbf{u}_k-\mathbf{u}_k^*)\mathbf{e}_k, 
 \label{eq:actorWeights}
 \end{align}
 where $\ell$ is the actor learning rate. 
 \\
 The complete policy iteration solution process for the leader-follower problem is detailed out in Algorithm \ref{alg:ModelFreeTracking}. %
 %
 \begin{algorithm2e}{
     \caption{\label{alg:ModelFreeTracking} Model-free actor-critic reinforcement learning using the policy iteration solution.}
     \DontPrintSemicolon
     \KwIn{Sampling-time $T_s,$ $\mathbf{Q},~\text{and}~\mathbf{R}$ }
     \KwOut{Error trajectory $\mathbf{e}_k,$ for $k=0,1,\ldots$}
     % \KwData{Map representation using occupancy grid technique}
     % \KwResult{output******************************}
     \Begin{
         $k=0, r = 0$ \tcc*[h]{Discrete time and policy indices}\;
         $\eta = (n+m)(n+m+1)/2$\;
         Initialize $\mathbf{P}^{[0]}$ \tcc*[h]{Positive definite}\;
                 Set offset distance $d$\;
                 Given approximate initial poses of leader and follower, compute $\mathbf{e}_0$ using error model~\eqref{eq:stateError}\;
                 Compute follower's input $\mathbf{u}_0^{[0]}$ using policy~\eqref{eq:actorWeightsPolicy}\;
         \Repeat(\tcc*[h]{Main timing loop}){Tracking errors are zero}
         {
             Find $\mathbf{e}_{k+1}$ using~\eqref{eq:stateError}\;
             Compute policy $\mathbf{u}_{k+1}^{[r]}$ using~\eqref{eq:actorWeightsPolicy}\;
             %Evaluate and record Equation~\eqref{eq:modelFreeMatrixSolution}\;
             \If{[$(k+1)~\mathrm{modulo}~\eta]==0$ }
             {
                 $r\leftarrow r+1$\tcc*[h]{Evaluate policy}using~\eqref{eq:modelFreePolicy}\;
                 Solve for the critic-weights $\bm{\omega_c}$ using~\eqref{eq:criticWeights}eights}\;
                 Solve for the actor-weights $\bm{\omega_a}$ using ~\eqref{eq:actorWeights}\;\;
                 Construct matrix $\mathbf{P}^{[r]}$ using vector $\bm{\omega_c}$\;
 %                \eIf{$\|\mathbf{P}^{[r]} - \mathbf{P}^{[r+1]}\|<\varepsilon$}{Set $\mathbf{u}_{k+1}^*\leftarrow\mathbf{u}_{k+1}^{[r]}$}{$k\leftarrow k+1$ }
             }
 %        {
 %                $k\leftarrow k+1$
 %            }
         $k\leftarrow k+1$
         }
     }
 \end{algorithm2e}

@@

 \begin{figure*}[htbp]%
 \subfigure[][]{%
    \label{fig:trajectoryRandom}%
    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/trajectoryRandomPathDistance.eps} }
	\subfigure[][]{%    
    \label{fig:euclideanDistance}%
    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/euclideanDistance.eps} }
\subfigure[][]{%
    \label{fig:stateErrorRandom}%
    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/stateErrorRandomPathDistance.eps} }
 \subfigure[][]{%
    \label{fig:controlInputsRandom}%
    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/controlInputRandomPathDistance.eps} }
 \subfigure[][]{%
    \label{fig:weightRandomDistance}%
    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/weightRandomPathDistance.eps} }
     \subfigure[][]{%
    \label{fig:actorWeightRandomDistance}%
    \includegraphics[width=0.48\textwidth,height=0.25\textheight]{figs/coppelia/firstScenario/weightActor.eps} }
\caption[Leader-follower performance for random trajectory.]{Performance in tracking random trajectory: 
  \subref{fig:trajectoryRandom} leader-follower trajectories,~\subref{fig:stateErrorRandom} state error,~\subref{fig:controlInputsRandom} linear speed and steering angle of the follower; and    \subref{fig:weightRandomDistance} learning weights.}%
  \label{fig:peformanceRandomTrajectory}%
\end{figure*}
